Artin Group Presentations Arising from Cluster Algebras

### 2014-09-02 Paper.tex
tried to move diagrams, but failed
made all of greg's comments for sections 3,4 except first

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{longfig}[thm]{Figure}

%\usepackage[all]{xy}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{note}[thm]{Notation}
\newtheorem{ex}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
%\newcommand\fri{s_4^{-1}}
%\newcommand\fr{s_4}
%\newcommand\tri{s_3^{-1}}
%\newcommand\tr{s_3}
%\newcommand\twi{s_2^{-1}}
%\newcommand\tw{s_2}
%\newcommand\oni{s_1^{-1}}
%\newcommand\on{s_1}
\newcommand\V{V(\Gamma)}

@@

\begin{figure}[h]\label{fig:cycle_types}
\hspace*{-1.2cm}
\begin{tikzpicture}[baseline=-0.5ex]
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
    %
    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
    %
    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (ul) -- node[left]{1}(lu)
  ;
  \draw
  (dr) -- node[right]{1}(rd)
  ;
  \draw
  (lu) -- node[left]{1}(ld)
  ;
  \draw
  (ru) -- node[right]{1}(rd)
  ;
  \draw
  (ur) -- node[right]{1}(ru)
  ;
  \draw
  (dl) -- node[left]{1}(ld)
  ;
  \draw[dotted]
  (dl) -- (dr)
  ;
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (5,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (dl) -- node[left]{2}(ul)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;
  \draw
  (ur) -- node[right]{2} (dr)
  ;
   \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (9,0)
  {
    && |[name = u]|\circ& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw
  (u) -- node[right] {2} (dr)
  ;
  \draw
  (dl) -- node[left]{2}(u)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;

   \end{tikzpicture}
\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
\end{figure}
\end{prop}

@@

\begin{figure}
\label{fig:local_three}
\begin{enumerate}[(a)]
\item
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (dr) to node[right] {1} (u)
  ;
  \draw[->]
  (dl)to node[left]{1}(u)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
   (u)to node[right] {1} (dr)
  ;
  \draw[->]
  (u) to node[left]{1}(dl)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
   \end{tikzpicture}
\item
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (u) to node[right] {1} (dr)
  ;
  \draw[->]
  (dl)to node[left]{1}(u)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (dr) to node[right] {1}(u)
  ;
  \draw[->]
  (u) to node[left]{1}(dl)
  ;
  \draw[->]
  (dl) to node[below]{1}(dr)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
   \end{tikzpicture}

@@

\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
\end{figure}

@@

\label{fig:cycle_types_a}

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\bullet& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[left]{2}(dl)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\draw[->]
  (dl) to node[above]{2} (ur)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
    \end{tikzpicture}

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\circ & |[name = ur]|\bullet\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (dr) to node[right]{2} (ur)
  ;
\draw[->]
  (ul) to node[above]{2} (dr)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .3 5 cm] at (ul){$C'$};
    \end{tikzpicture}
    \end{enumerate}
\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
\end{figure}

\begin{figure}
\label{fig:cycle_types_b}
\begin{enumerate}
   \item[(i)]
   \begin{tikzpicture}[baseline=-0.5ex]
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
    %
    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
    %
    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
  };
\draw[->]
  (ml) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[above]{1}(um)
  ;
  \draw[->]
  (um) to node[above]{1}(ur)
  ;
  \draw[->]
  (ur) [bend left] to (mr)
  ;
  \draw[->]
  (mr) [bend left] to (dr)
  ;
  \draw[->]
  (dr) to node[below]{1}(dm)
  ;
  \draw[->]
  (dm) to node[below]{1}(dl)
  ;
  \draw[->]
  (dl) to node[below]{1}(ml)
  ;
    \node at (ml.west){$k$};
    \node at (ul.north){1};
    \node at (um.north){2};
    \node at (dm.south){$h-1$};
    \node at (dl.south){$h$};
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
  {
    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
    %
    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
    %
    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
  };
\draw[->]
  (ul) to node[above] {1} (ml)
  ;
  \draw[->]
  (ul) to node[above]{1}(um)
  ;
  \draw[->]
  (um) to node[above]{1}(ur)
  ;
  \draw[->]
  (ur) [bend left] to (mr)
  ;
  \draw[->]
  (mr) [bend left] to (dr)
  ;
  \draw[->]
  (dr) to node[below]{1}(dm)
  ;
  \draw[->]
  (dm) to node[below]{1}(dl)
  ;
  \draw[->]
  (ml) to node[below]{1}(dl)
  ;
  \draw[->]
  (dl) to node[right]{1}(ul)
  ;
    \node at (ml.west){$k$};
    \node at (ul.north){1};
    \node at (um.north){2};
    \node at (dm.south){$h-1$};
    \node at (dl.south){$h$};

@@

\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
\end{figure}

\begin{lem}\label{lem:chordless_cycles}
\cite[Lemma 2.5]{BM13} 
Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ In figures \ref{fig:cycle_types_a} and \ref{fig:cycle_types_b} we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle. Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.

@@

\begin{defn}
\cite[Beginning of section 1.2]{C06}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a symmetric matrix whose entries can take values in the integers or infinity, we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}} = \langle x_j,x_i \rangle^{M_{i,j}} \text{ for all } i,j \text{ with } M_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@

\begin{rem}
Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the Artin group corresponding to that Dynkin diagram. This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(T2),$ which define the Artin group.
\end{rem}

@@

\begin{proof}
The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.  We show that $t_i$ and $t_j$ satisfy the $(T2^\prime)$ relations by checking each case.  Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in the figure in Corollary \ref{local_three_picture}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in the figure in Corollary \ref{local_three_picture}.

@@

\begin{table} \label{table1}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (R4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$ \\ \hline

@@

\begin{table} \label{table2}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (T4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $s_{2}s_{1}s_{2}^{-1}s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}s_{2}s_{1}s_{2}^{-1}$ \\ \hline

>>>>

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
%\usepackage[all]{xy}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{note}[thm]{Notation}
\newtheorem{ex}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
%\newcommand\fri{s_4^{-1}}
%\newcommand\fr{s_4}
%\newcommand\tri{s_3^{-1}}
%\newcommand\tr{s_3}
%\newcommand\twi{s_2^{-1}}
%\newcommand\tw{s_2}
%\newcommand\oni{s_1^{-1}}
%\newcommand\on{s_1}
\newcommand\V{V(\Gamma)}

@@

\begin{figure}[h]
\hspace*{-1.2cm}
\begin{tikzpicture}[baseline=-0.5ex]
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
    %
    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
    %
    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (ul) -- node[left]{1}(lu)
  ;
  \draw
  (dr) -- node[right]{1}(rd)
  ;
  \draw
  (lu) -- node[left]{1}(ld)
  ;
  \draw
  (ru) -- node[right]{1}(rd)
  ;
  \draw
  (ur) -- node[right]{1}(ru)
  ;
  \draw
  (dl) -- node[left]{1}(ld)
  ;
  \draw[dotted]
  (dl) -- (dr)
  ;
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (5,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (dl) -- node[left]{2}(ul)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;
  \draw
  (ur) -- node[right]{2} (dr)
  ;
   \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (9,0)
  {
    && |[name = u]|\circ& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw
  (u) -- node[right] {2} (dr)
  ;
  \draw
  (dl) -- node[left]{2}(u)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;

   \end{tikzpicture}
   \label{fig:cycle_types}
\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
\end{figure}
\end{prop}

@@

\begin{figure}
\begin{enumerate}[(a)]
\item
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (dr) to node[right] {1} (u)
  ;
  \draw[->]
  (dl)to node[left]{1}(u)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
   (u)to node[right] {1} (dr)
  ;
  \draw[->]
  (u) to node[left]{1}(dl)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
   \end{tikzpicture}
\item
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (u) to node[right] {1} (dr)
  ;
  \draw[->]
  (dl)to node[left]{1}(u)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (dr) to node[right] {1}(u)
  ;
  \draw[->]
  (u) to node[left]{1}(dl)
  ;
  \draw[->]
  (dl) to node[below]{1}(dr)
  ;
  \node [yshift = .4 cm] at (u){k};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
   \end{tikzpicture}

@@

\label{fig:local_three}
\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
\end{figure}

@@

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\bullet& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[left]{2}(dl)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
\draw[->]
  (dl) to node[above]{2} (ur)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
    \end{tikzpicture}
    \end{enumerate}

\label{fig:cycle_types_a}
\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
\end{figure}

\begin{figure}
\begin{enumerate}

@@

   \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
  {
    & |[name = ul]|\circ & |[name = ur]|\bullet\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ur) to node[above] {1} (ul)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (dr) to node[right]{2} (ur)
  ;
\draw[->]
  (ul) to node[above]{2} (dr)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
  \node [yshift = -.95 cm,xshift = .3 5 cm] at (ul){$C'$};
    \end{tikzpicture}
   \item[(i)]
   \begin{tikzpicture}[baseline=-0.5ex]
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
    %
    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
    %
    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
  };
\draw[->]
  (ml) to node[above] {1} (ul)
  ;
  \draw[->]
  (ul) to node[above]{1}(um)
  ;
  \draw[->]
  (um) to node[above]{1}(ur)
  ;
  \draw[->]
  (ur) [bend left] to (mr)
  ;
  \draw[->]
  (mr) [bend left] to (dr)
  ;
  \draw[->]
  (dr) to node[below]{1}(dm)
  ;
  \draw[->]
  (dm) to node[below]{1}(dl)
  ;
  \draw[->]
  (dl) to node[below]{1}(ml)
  ;
    \node at (ml.west){$k$};
    \node at (ul.north){1};
    \node at (um.north){2};
    \node at (dm.south){$h-1$};
    \node at (dl.south){$h$};
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
  {
    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
    %
    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
    %
    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
  };
\draw[->]
  (ul) to node[above] {1} (ml)
  ;
  \draw[->]
  (ul) to node[above]{1}(um)
  ;
  \draw[->]
  (um) to node[above]{1}(ur)
  ;
  \draw[->]
  (ur) [bend left] to (mr)
  ;
  \draw[->]
  (mr) [bend left] to (dr)
  ;
  \draw[->]
  (dr) to node[below]{1}(dm)
  ;
  \draw[->]
  (dm) to node[below]{1}(dl)
  ;
  \draw[->]
  (ml) to node[below]{1}(dl)
  ;
  \draw[->]
  (dl) to node[right]{1}(ul)
  ;
    \node at (ml.west){$k$};
    \node at (ul.north){1};
    \node at (um.north){2};
    \node at (dm.south){$h-1$};
    \node at (dl.south){$h$};

@@

\label{fig:cycle_types_b}
\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
\end{figure}

\begin{lem}\label{lem:chordless_cycles}
\cite[Lemma 2.5]{BM13} 
Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ In Figure \ref{fig:cycle_types_a} and Figure \ref{fig:cycle_types_b} we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle. Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.

@@

\begin{defn}
\cite[Beginning of section 1.2]{C06}
Let $Sym_n(R)$ denote the set of $n \times n$ symmetric matrices with entries in $R$. For $M \in Sym_n(\mathbb Z \cup \infty)$ a symmetric matrix whose entries can take values in the integers or infinity, we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}} = \langle x_j,x_i \rangle^{M_{i,j}} \text{ for all } i,j \text{ with } M_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@

\begin{rem}
Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the Artin group corresponding to that Dynkin diagram. This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relations of the form $(T2),$ which define the Artin group.
\end{rem}

@@

\begin{proof}
The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Figure \ref{fig:local_three}.  We show that $t_i$ and $t_j$ satisfy the $(T2^\prime)$ relations by checking each case.  Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in Figure \ref{fig:local_three}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in Figure \ref{fig:local_three}.

@@

\begin{table}[!h] \label{table1}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (R4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$ \\ \hline

@@

\begin{table}[!h] \label{table2}
\begin{tabular}{| p{3.5cm} | p{7cm} |}
\hline
Subdiagram & (T4) Relation \\ \hline
\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $s_{2}s_{1}s_{2}^{-1}s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}s_{2}s_{1}s_{2}^{-1}$ \\ \hline
